---
title: "Digital Capabilities Report"
author: "Gabriele"
date: "2023-02-05"
output: 
  pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```


```{r Load, include = FALSE}
#PDF Guide https://bookdown.org/yihui/rmarkdown/pdf-document.html
library(tidyverse)
library(readxl)
library(ggplot2)
library(janitor)
library(scales)

raw_data <- read_excel("data.xlsx", sheet = "Scopus", range = "A1:R1102", na = "") %>% clean_names()

df <-
  raw_data %>% 
  mutate(discipline = case_when(field == "ACCOUNTING" ~ "Accounting",
                                field == "FINANCE" ~ "Finance",
                                field == "INFO MAN" ~ "Information Systems",
                                field == "MARKETING" ~ "Marketing",
                                str_detect(field, "OPERATION") ~ "Operations",
                                (field == "ENTREPRENEURSHIP" | field == "IB") ~ "Entrepreneurship and IB",
                                (field == "HR" | field == "ORGANISATION STUDIES" | field == "MANAGEMENT") ~ "Management",
                                (field == "STRATEGY" | field == "INNOVATION") ~ "Strategy and Innovation",
                                .default = NA))
```

## General Observations

This report provides a bunch of information about the dataset of `r raw_data %>% count(field, sort = TRUE, ) %>% tally(n)` articles for our review of the digital capabilities literature. We are focusing in the following disciplines: `r df %>% distinct(discipline)`. 

```{r cars}
x <- df %>% count(discipline, included) %>% spread(key = included, value = n) %>% 
  mutate(percentage = percent(Yes / (No + Yes), accuracy = 0.1)) %>% arrange(discipline)
knitr::kable(x, 
  col.names = str_to_title(names(x)),
  caption = "Articles Inspected by Discipline",
  format.args = list()
)

x <- df %>% distinct(discipline, field) %>% arrange(discipline)
knitr::kable(x, 
  col.names = str_to_title(names(x)),
  caption = "Mapping of Scopus Fields to Disciplines",
  format.args = list()
)
```

\pagebreak
For each discipline we examined the following number of journals in the 4 and 4* range:

```{r articles}
x <- df %>% distinct(source_title, discipline, rating) %>% count(discipline, rating) %>% 
  spread(key = rating, value = n) %>% arrange(discipline)
knitr::kable(x, 
  col.names = str_to_title(names(x)),
  caption = "Articles Inspected by Discipline",
  format.args = list()
)
```

Predictably the number of articles related to IT capabilities, IT-enabled capabilities and digital capabilities has grown over time in every discipline. 

```{r yearly plot, fig.cap = "Growth of Articles from 1990 to 2022"}
df %>% filter(year != "2023") %>% 
  group_by(discipline) %>% 
  count(year, sort = TRUE) %>%
  ggplot(aes(x=year, y=n, group=discipline)) +
  geom_line(aes(linetype=discipline, color=discipline)) +
  theme(legend.position="top") +
  theme(legend.title=element_blank())
```

